A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-21 4_method.tex
properties of significance measure

\paragraph{Bead counts}
In order to apply the beading strategy to the VQ
we assign each significant node $v$ of the skeleton a bead count $v.B^*$ which is initialized to $b(R(v))$, but it is modified in order to prevent discontinuities and remaining gaps.

>>>>

\subsubsection{Properties of significant regions}
A node in the graph can have at most two significant edges.
For a node in the VD $v$ with a support of three points on the outline polygon $p_1, p_2, p_3$, the bisector angles $\angle{p_1vp_2} + \angle{p_2vp_3} + \angle{p_3vp_1} = 360\degree$, so if two angles are more than $\alpha_\text{max} > 120\degree$ the third one needs to be smaller than $360\degree - 2\alpha_\text{max} < 120\degree$ and therefore nonsignificant.
% However, because of some filtering operations this property does not neccesarily hold for the markings.
The extra edges added to the VD to form the VQ can never be significant because their bisector angle is \SI{0}{\degree} by definition,
so the nodes of the VQ also have at most two significant edges.

A saddle point is always marked.
When going from one local maximum to another we must pass through a significant region.
You will either go through the marked region of a discretized parabola or of a segment with two polygonal vertices as support.
This menas that the feature radius function in between marked regions is monotonic.
This means that when propagating beadings downward from marked regions they can never conflict in the middle - they will always conflict at either marked region.

From any node in the graph which is not a saddle point there is only a single edge going upward.
\todo{Explanation / proof needed.}
%See VoronoiQuadrangulation::filterUnmarkedRegions
This means that walking up the graph from a marked region to a local maximum follows a single path without branchings.

The two downward edges from a branch point cannot both be significant.
A branch point which is not a local maximum generated by the support points $p_1, p_2, p_3$ has bisector angles such that $\triangle p_1 p_2 p_3$ has its circumcentre $v$ outside of the triangle, because otherwise the feature radius decreases in all directions.
This means that all support points lie within a \SI{180}{\degree} range around the node. 
Suppose the one edge going upward is generated by $p_1$ and $p_3$.
Then the bisector angle $\angle p_1 v p_3 < 180\degree$ and $\angle p_1 v p_2 + \angle p_2 v p_3 < 180\degree$,
so if $\angle p_1 v p_2 < 120\degree$ then $\angle p_2 v p_3 < 60\degree$ and is therefore not significant. 
%so at most either of $\angle p_1 v p_2$ and $\angle p_2 v p_3$ has a significant bisector angle.

\subsubsection{Bead counts}
In order to apply the beading strategy to the VQ
we assign each significant node $v$ of the skeleton a bead count $v.B^*$ which is initialized to $b(R(v))$, but it is modified in order to prevent discontinuities and remaining gaps.
